\documentclass{cookbook}

\begin{document}
\special{papersize=149mm,210mm}% for dvips to use
\thispagestyle{empty}

\begin{center}
	\Huge THE F'F'FUSS FREE FOOD FILE%
\end{center}

\vfill

\begin{center}
	Arthur J. Bloatworthy III\\
	Bone Head Publishing
\end{center}

\clearpage

\strut% So the vfill has something to push against
\vfill

\begin{quotation}
\begin{rmfamily}
	The author of this book
	accepts no responsibility
	for damages resulting from its use
	and makes no warranty or
	representation of
	any implied warranty of merchantability
	or fitness for a particular purpose.
	This book is provided as is
	and you assume all risks
	when using it.
\par
\bigskip
	Copyright \copyright\ 1997 by
	Joe J Collins,
	trading as
	Arthur J. Bloatworthy III,
	Bone Head Publishing and
	F'F'Industries.
	All rights reserved.
	No part of this publication may be reproduced,
	stored in a retrieval system,
	or transmitted,
	in any form or by any means,
	electronic,
	mechanical,
	photocopying,
	recording,
	or otherwise,
	without the prior written permission
	of the publisher;
	Joe J Collins.
\end{rmfamily}
\end{quotation}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\notes{Foreword}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The menus provide four different meals
for each week.
You make a double amount for one meal
and then have the rest for the next meal,
so a micro-wave oven would be useful.
One meal in every seven is some kind of quick
or easily prepared meal.
The ingredients for each menu are accumulated
into a fortnightly shopping list.
The shopping lists
and check lists cover two weeks food
(for main meals)
for two people.
Most of them are one pan meals.
You will need:

\begin{itemize}
	\item 3 litre \cass.
	\item 2 litre \pan.
	\item 35 cm \wok.
	\item 3 litre mixing bowl.
\end{itemize}

Vegetables will not last for more than about a week,
so there is a mid fortnight vegetable shopping list.
Vegetables will last better if kept in an air tight box,
lined with a tea towel,
in the fridge.
Meat will need to be frozen
and
dairy products will need to be refridgerated.
No other shopping is required.

All measurements using spoons are heaped,
as much as they can be heaped.

\begin{itemize}
	\item[tsp] teaspoon.            % Nominally 5ml
	\item[dsp] dessert spoon.       % Nominally 10ml
	\item[tbsp] table spoon.        % Nominally 20ml
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tableofcontents{Fuss Free Food File}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\season{Winter}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{Beginning of Winter}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Meat stew and dumplings}%
{%
	\index{Stew!Meat and dumplings}%
	\index{Dumplings}%
	\st	\spud.
	\st	In a \wok fry
		\ve{350}{g}{onions}{chopped},
		\me{400}{g}{meat}{sliced},
		\ve{400}{g}{carrots}{chopped}
		and
		\ve{400}{g}{celery}{chopped}
		in
		\ch{2}{tbsp}{oil}{}
		until meat done.
	\st	Stir in
		\gr{75}{g}{tomato puree}{},
		\ch{0.5}{tsp}{chilli powder}{},
		\ch{1}{}{stock cube}{crumbled},
		\wa{500}{ml}{water}{}
		and
		simmer for 50 minutes.
	\st	In a \bowl mix
		\ch{75}{g}{self raising flour}{},
		\ch{75}{g}{suet}{},
		\ch{0.5}{tsp}{mixed herbs}{}
		and
		\wa{100}{ml}{water}{}
		and knead into 8 balls.
		Put balls in stew, cover and
		simmer for 15 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Onion and tomato lasagna}%
{%
	\index{Lasagna!Onion and tomato}%
	\st	In a \wok fry
		\ve{700}{g}{onions}{chopped}
		in
		\ch{2}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\gr{400}{g}{canned tomatoes}{chopped}
		and warm through.
	\st	In a \cass layer
		\gr{200}{g}{lasagna}{},
		tomato mix and
		\da{150}{g}{cheese}{grated} 3 times.
	\st	In a bowl mix
		\da{300}{ml}{soured cream}{}
		with
		\da{100}{ml}{milk}{} and pour on top of the lasagna.
	\st	Bake \med for 50 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Chicken with cabbage and peanuts}%
{%
	\st	\noodles.
	\st	In a \wok fry
		\gr{3}{tbsp}{peanuts}{}
		in 
		\ch{2}{tbsp}{oil}{} then remove.
	\st	Fry 
		\ve{2}{}{red chillis}{}
		in the oil for 2 minutes.
	\st	Stir in
		\me{300}{g}{chicken}{sliced}
		and
		\ve{750}{g}{cabbage}{sliced},
		fry until meat is done.
	\st	Stir in 
		\ch{1}{tbsp}{black bean sauce}{}
		and fry for 2 minutes.
	\st	Sprinkle with the peanuts.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Beans and fried eggs in pitta}%
{%
	\st	In a \pan warm
		\gr{400}{g}{baked beans}{}.
	\st	In a \wok fry
		\da{2}{}{eggs}{}
		in
		\ch{1}{tbsp}{oil}{}.
	\st	Grill
		\gr{4}{}{pitta bread}{}.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Egg and vegetable curry}%
{%
	\index{Curry!Egg and vegetable}
	\st	In a \pan hard boil
		\da{4}{}{eggs}{},
		peel them and chop them in half.
	\st	\rice.
	\st	In a \wok fry
		\ve{350}{g}{onions}{chopped}
		in 
		\ch{2}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ch{1}{tbsp}{curry powder}{}
		and
		\ch{2}{tsp}{mustard seed}{}
		and fry until mustard seeds start to pop.
	\st	Stir in
		\ch{2}{tbsp}{flour}{} until it is all absorbed.
	\st	Stir in
		\gr{150}{g}{tomato puree}{},
		\ch{50}{g}{creamed coconut}{crumbled}
		and
		\wa{400}{ml}{water}{}
		and warm through.
	\st	Stir in
		\ve{400}{g}{mange tout}{halved}
		and
		the eggs
		and simmer for 10 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Lentil shepherds pie}%
{%
	\index{Shepherds Pie!Lentil}
	\st	In a \pan boil
		\ve{1000}{g}{potatoes}{} then mash.
	\st	In a \wok fry
		\ve{700}{g}{onions}{chopped},
		\ve{5}{cloves}{garlic}{crushed},
		\ve{400}{g}{celery}{chopped} 
		and 
		\ve{200}{g}{carrots}{sliced} 
		in
		\ch{2}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\gr{250}{g}{green lentils}{},
		\ch{1}{}{stock cube}{crumbled},
		\gr{75}{g}{tomato puree}{},
		\wa{650}{ml}{water}{},
		\ch{1}{tsp}{marjoram}{},
		\ch{1}{tsp}{ground cumin}{}
		and 
		\ch{2}{tsp}{ground coriander}{},
		bring to boil,
		then simmer for 30 minutes.
	\st	Take off heat and stir in
		\ch{3}{tsp}{miso}{}.
		Put in a \cass, cover with the potatoes
		and sprinkle with
		\ch{50}{g}{sunflower seed}{}
		then bake \med for 30 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Chickpea risotto}%
{%
	\index{Risotto!Chickpea}
	\st	In a \wok fry
		\ve{400}{g}{onions}{chopped}
		and
		\ve{4}{cloves}{garlic}{crushed}
		in
		\ch{2}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ve{250}{g}{spinach}{hacked}
		and cook until wilted.
	\st	Stir in
		\gr{400}{g}{canned chick peas}{drained},
		\gr{75}{g}{raisins}{},
		\ch{1}{}{stock cube}{crumbled},
		\ve{1000}{g}{sweet potatoes}{sliced},
		\gr{2*400}{g}{canned tomatoes}{chopped}
		and
		\ve{1}{}{red chilli}{chopped},
		and warm through.
	\st	Stir in
		\gr{400}{g}{rice}{}
		and
		\wa{750}{ml}{water}{},
		simmer until rice is done.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Tortellini and parmesan cheese}%
{%
	\st	\halfpasta{tortellini}
	\st	Sprinkle with
		\ch{20}{g}{grated parmesan}{}.
}%
\end{menu}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Aubergine and peppers}%
{%
	\st	\spud.
	\st	In a \wok fry
		\ve{350}{g}{onions}{sliced}
		and
		\ve{4}{cloves}{garlic}{crushed}
		in
		\ch{4}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ve{150}{g}{red peppers}{sliced},
		\ve{150}{g}{green peppers}{sliced},
		\ve{400}{g}{aubergine}{sliced},
		\ve{400}{g}{courgettes}{sliced},
		\gr{150}{g}{tomato puree}{},
		\wa{100}{ml}{water}{}
		and
		\ve{400}{g}{tomatoes}{chopped},
		and bring to the boil.
	\st	Put in a \cass and bake \med for 40 
minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Potatoes Russian style}%
{%
	\index{Style!Russian potatoes}
	\st	In a \pan boil
		\ve{3000}{g}{potatoes}{cubed}
		until not quite done
		then drain.
	\st	Stir in
		\da{1}{large carton}{cottage cheese}{},
		\da{300}{ml}{sour cream}{},
		\da{150}{g}{cheese}{grated}
		and
		\ve{4}{cloves}{garlic}{crushed}.
	\st	Put in \cass and bake \med for 1 hour.
 }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Lentils and spicy sausage}%
{%
	\st	\rice.
	\st	In a \wok fry
		\ve{350}{g}{onions}{chopped},
		\ve{4}{cloves}{garlic}{crushed}
		and
		\me{100}{g}{bacon}{chopped}
		in
		\ch{3}{tbsp}{oil}{}
		until bacon done.
	\st	Stir in
		\gr{250}{g}{lentils}{},
		\gr{2*400}{g}{canned tomatoes}{},
		\me{250}{g}{spicy sausage}{sliced},
		\ch{1}{tsp}{chilli powder}{}
		and
		\wa{400}{ml}{water}{}
		and simmer for 25 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Baked bean pizza}%
{%
	\index{Pizza!Baked bean}%
	\st	Spread
		\gr{400}{g}{canned baked beans}{}
		on
		\gr{2*9}{inch}{pizza bases}{}
		cover with
		\da{100}{g}{cheese}{grated}
		and spinkle on
		\ch{1}{tsp}{mixed herbs}{}.
	\st	Bake \hi 20 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Mushroom stew}%
{%
	\index{Stew!Mushroom}
	\st	In a \wok fry
		\ve{375}{g}{onions}{chopped}
		in
		\ch{2}{tbsp}{oil}{}
		until soft. 
	\st	Stir in
		\ve{600}{g}{mushrooms}{}
		and
		\ve{4}{cloves}{garlic}{crushed}
		and cook until mushrooms start to wilt.
	\st	Stir in
		\gr{150}{g}{pearl barley}{},
		\ch{4}{tbsp}{soy sauce}{},
		\ch{5}{tbsp}{sherry}{},
		\ch{1}{}{stock cube}{crumbled}
		and
		\wa{450}{ml}{water}{}
		and simmer for 25 minutes.
	\st	\pasta{tagliatelli}.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Beans Caribbean style}%
{%
	\index{Style!Carribbean beans}
	\st	In a \wok heat up
		\gr{400}{g}{canned kidney beans}{}
		and
		\gr{400}{g}{canned chick peas}{}
		in their liquid.
	\st	Stir in
		\ve{350}{g}{onions}{chopped},
		\ve{150}{g}{green peppers}{chopped}
		and
		\ve{3}{cloves}{garlic}{crushed},
		cover and simmer for 50 minutes.
	\st	Stir in
		\gr{150}{g}{tomato puree}{}
		and
		\ch{2}{tbsp}{oil}{},
		cover and simmer for 30 minutes.
		(Keep the beans covered with liquid,
		by adding more water if necessary.) 
	\st	\couscous.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Tomatoes Indian style}%
{%
	\index{Style!Indian tomatoes}
	\st	\rice.
	\st	In a \wok heat
		\ch{4}{tbsp}{oil}{},
		\ch{0.5}{tsp}{asafetida}{},
		and
		\ch{2}{tsp}{cumin seeds}{}
		until
		the cumin sizzles.
	\st	Stir in
		\ve{1}{}{red chilli}{chopped}
		and
		\ve{350}{g}{onions}{chopped}
		and
		fry until soft.
	\st	Stir in
		\ve{1}{kg}{tomatoes}{chopped}
		and
		simmer for 10 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Bacon and mushroom pasta}
{%
	\st	\halfpasta{tagliatelli}.
	\st	In a \wok fry \me{150}{g}{bacon}{chopped}
		and
		\ve{200}{g}{mushrooms}{sliced}
		in
		\ch{1}{tbsp}{oil}{} for 5 minutes.
	\st	Stir in the pasta (cooked and drained)
		and \da{100}{g}{cheese}{grated}
		and warm through.
}%

\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Aubergine and chickpeas}%
{%
	\st	In a \wok fry
		\ve{700}{g}{onions}{chopped} in
		\gr{7}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ve{1000}{g}{aubergine}{cubed}
		and fry until aubergines are done.
	\st	Stir in
		\gr{400}{g}{canned ckickpeas}{drained},
		\gr{400}{g}{canned tomatoes}{chopped}
		and
		\gr{1}{}{stock cube}{crumbled}.
		Put in \cass and bake \med 40 minutes.
	\st	\rice.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Meat goulash}%
{%
	\st	In a \wok fry
		\ve{400}{g}{onions}{chopped},
		\ve{2}{cloves}{garlic}{crushed}
		and
		\me{400}{g}{meat}{sliced}
		in
		\ch{4}{tbsp}{oil}{}
		until meat sealed.
	\st	Stir in
		\ch{1}{tbsp}{flour}{},
		\ch{1}{tsp}{paprika}{},
		\gr{400}{g}{canned tomatoes}{chopped}
		and
		\ve{150}{g}{red peppers}{sliced}.
	\st	Put in \cass and bake \lo 50 minutes.
	\st	\spud.
	\st	Stir in
		\da{150}{ml}{sour cream}{}
		to the goulash
		before serving.
}%
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Tagliatelli and mushroom sauce}%
{%
	\st	\pasta{tagliatelli}.
	\st	In a \wok fry
		\ve{400}{g}{onions}{chopped}
		in 
		\gr{3}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ve{700}{g}{mushrooms}{chopped},
		\ch{2}{tbsp}{sherry}{},
		\wa{200}{ml}{water}{boiling}
		and
		\ch{2}{tsp}{nutmeg}{grated},
		cover and simmer for 3 minutes.
	\st	Stir in
		\da{140}{ml}{single cream}{}
		and the drained pasta
		and warm through.
	\st	Sprinkle with
		\gr{50}{g}{grated parmesan}{}
		and
		\da{200}{g}{cheddar cheese}{grated}.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Garlic beans}%
{%
	\st	In a \wok fry
		\ve{3}{cloves}{garlic}{crushed}
		in
		\ch{1}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\gr{400}{g}{canned baked beans}{}
		and warm through.
	\st	Serve with
		\gr{4}{}{pita bread}{warmed}.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Sweet and Sour Celery}
{
	\st	\rice.
	\st	In a \wok fry
		\ve{400}{g}{celery}{sliced}
		and
		\ve{200}{g}{onions}{chopped}
		in
		\ch{4}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\gr{400}{g}{canned tomatoes}{chopped}
		and simmer for 10 minutes.
	\st	Stir in
		\ch{3}{tbsp}{wine vinegar}{},
		\ch{1}{tbsp}{sugar}{},
		\ch{4}{}{cloves}{},
		\ch{1}{tsp}{ground cinnamon}{},
		\gr{200}{g}{olives}{}
		and the celery
		and simmer for 10 minutes.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Sausage and potatoes German style}
{%
	\index{Style!German sausage and potatoes}%
	\st	In a \pan boil
		\ve{1500}{g}{potatoes}{chopped}
		until nearly done.
	\st	Put in
		\ve{500}{g}{eating apples}{}
		and simmer until apples soft.
	\st	Drain and mash with
		\ve{25}{g}{butter}{}.
	\st	Grill
		\me{500}{g}{sausages}{}
		and serve with the potatoes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Tomato spaghetti}
{%
	\index{Spaghetti!Tomato}%
	\st	In a \wok fry
		\ve{300}{g}{onions}{chopped}
		and
		\ve{3}{cloves}{garlic}{crushed}
		in
		\ch{3}{tbsp}{oil}{}
		for 1 minute.
	\st	Stir in
		\gr{2*400}{g}{canned tomatoes}{chopped},
		\gr{2}{tsp}{sugar}{},
		the juice of \ve{1}{}{lemon}{},
		\ch{1}{tsp}{basil}{}
		and simmer for 30 minutes.
	\st	\pasta{spaghetti}.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Peas and bacon}
{%
	\st	In a \wok fry
		\ve{200}{g}{onions}{chopped},
		\me{250}{g}{bacon}{chopped}
		in
		\gr{1}{tbsp}{oil}{}
		until browned.
	\st	Stir in
		\ve{800}{g}{frozen peas}{}
		and warm through.
}%
\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{Winter Solstice}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Vegetable mousaka}
{%
	\st	In a \pan boil
		\ve{500}{g}{potatoes}{sliced}
		until soft,
		then drain.
	\st	In a \wok fry
		\ve{400}{g}{onions}{sliced}
		and
		\ve{1000}{g}{aubergine}{sliced}
		in 
		\ch{4}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ve{4}{cloves}{garlic}{crushed},
		\ve{100}{g}{mushrooms}{sliced},
		\ve{500}{g}{tomatoes}{chopped},
		\gr{150}{g}{tomato puree}{},
		\wa{3}{tbsp}{water}{}
		and
		\ch{1}{tsp}{mixed herbs}{},
		and simmer for 10 minutes.
	\st	Put everything in a \cass
		and bake \med 30 minutes.
	\st	In a \bowl beat together
		\da{2}{}{eggs}{}, 
		\da{150}{ml}{natural yoghurt}{}
		and 
		\da{200}{ml}{milk}{}.
		Pour on the \cass, spinkle with 
		\da{150}{g}{mature cheese}{grated}
		and bake \med 20 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Chickpea and spinach curry}
{%
	\index{Curry!Chickpea and spinach}
	\st	\rice.
	\st	In a \wok fry
		\ch{2}{tsp}{cumin seeds}{}
		in
		\ch{4}{tbsp}{oil}{}
		for 2 minutes.
	\st	Stir in
		\ve{4}{cloves}{garlic}{crushed}
		and
		\ve{400}{g}{onions}{chopped}
		and fry until until soft.
	\st	Stir in
		\ve{500}{g}{spinach}{hacked},
		\ve{500}{g}{mushrooms}{sliced},
		\gr{400}{g}{canned chickpeas}{drained},
		\ch{2}{tbsp}{soya sauce}{}
		and
		\ch{2}{tsp}{garam masala}{}
		and simmer until spinach wilts.
}%
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Courgettes and bacon}%
{%
	\st	\spud,
		then slice.
	\st	In a \wok fry
		\ve{400}{g}{courgettes}{sliced},
		\ve{400}{g}{onions}{sliced}
		and
		\ve{2}{cloves}{garlic}{crushed}.
		in
		\ch{2}{tbsp}{oil}{}
		until soft.
	\st	Stir in 
		\me{6}{rashers}{bacon}{chopped},
		\da{100}{g}{mature cheese}{grated},
		\da{2}{}{eggs}{beaten},
		and
		\da{4}{tbsp}{milk}{}.
		Layer in a \cass
		with the potatoes
		and bake \med 35 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Tagliatelli and olive oil}%
{%
	\st	\halfpasta{tagliatelli},
		save 150 ml of the water.
	\st	In a \wok fry
		\ve{4}{cloves}{garlic}{crushed},
		\ch{1}{}{bay leaf}{crumbled}
		and
		\ve{1}{}{red chilli}{chopped}
		in
		\ch{4}{tbsp}{olive oil}{}
		until garlic browns.
	\st	Stir in the tagliatelli,
		the water
		and
		\gr{200}{g}{olives}{}
		and simmer for 3 minutes.
	\st	Spinkle with
		\gr{50}{g}{grated parmesan}{}.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Chicken curry}% Short cut Rhodes
{%
	\index{Curry!Chicken}
	\st	\rice.
	\st	In a \wok fry
		\ve{350}{g}{onions}{chopped}
		\ve{2}{cloves}{garlic}{crushed}
		in 
		\ch{3}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ch{2}{tbsp}{curry powder}{},
		\me{400}{g}{chicken}{sliced}
		and cook until done.
	\st	Stir in
		\gr{400}{g}{canned evapourated milk}{}
		and simmer for 10 minutes,
		stirring constantly (it burns easily).
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Lentil and vegetable curry}
{%
	\index{Curry!Lentil and vegetable}
	\st	In a \pan in
		\wa{450}{ml}{water}{}
		cook
		\gr{225}{g}{red lentils}{}
		until soft.
	\st	In a \wok fry
		\ch{1}{tsp}{cumin seeds}{},
		\ch{1}{tsp}{mustard seeds}{},
		and
		\ch{1}{tsp}{cinnamon}{ground}
		in
		\ch{4}{tbsp}{oil}{}.
	\st	Stir in
		\ve{400}{g}{onion}{chopped},
		\ve{2}{cloves}{garlic}{crushed},
		\ve{100}{g}{carrots}{sliced},
		\ve{150}{g}{red peppers}{chopped}
		and
		\gr{400}{g}{canned tomatoes}{chopped},
		and simmer for 5 minutes.
	\st	Stir in
		the lentils,
		\ch{100}{g}{creamed coconut}{},
		\ch{1}{tbsp}{curry powder}{}, 
		\gr{2}{tbsp}{cashew nuts}{}
		and juice of
		\ve{1}{}{lemon}{}.
	\st	\couscous.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Sweet corn pizza}
{%
	\index{Pizza!Sweet corn}
	\st	On
		\gr{4*9}{inch}{pizza bases}{}
		spread
		\gr{300}{g}{tomato puree}{},
		\ve{400}{g}{tomatoes}{chopped},
		\gr{200}{g}{canned sweetcorn}{},
		\ve{150}{g}{green peppers}{chopped},
		\gr{100}{g}{anchovy fillets}{},
		\gr{200}{g}{pineapple chunks}{},
		\da{200}{g}{mature cheese}{grated}
		and
		\ch{2}{tsp}{oregano}{}.
	\st	Bake \hi 20 minutes or until golden.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Fish fingers and baked beans}
{%
	\st	In a \pan heat up
		\gr{400}{g}{canned baked beans}{}.
	\st	Grill
		\gr{8}{}{fish fingers}{}.
}%
\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Lentil dhansak}
{%
	\index{Curry!Lentil dhansak}
	\st	\rice.
	\st	In a \wok fry
		\ve{200}{g}{onion}{finely chopped},
		\ve{2}{cloves}{garlic}{crushed}
		and
		\ve{100}{g}{carrots}{sliced}
		until soft.
	\st	Stir in
		\ch{1}{tbsp}{curry powder}{}, 
		\ch{1}{tsp}{cumin seeds}{},
		\ch{1}{tsp}{mustard seeds}{}
		and
		\ch{5}{cm}{cinnamon stick}{}
		and fry for 2 minutes.
	\st	Stir in
		\ve{400}{g}{canned tomatoes}{chopped},
		\gr{2}{tbsp}{cashew nuts}{},
		\ch{120}{ml}{creamed coconut}{},
		\gr{225}{g}{red lentils}{}
		and 
		\ve{150}{g}{red peppers}{chopped}
		and simmer for 20 minutes.
	\st	Add juice of
		\ve{1}{}{lemon}{}
		and warm.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Spaghetti and pasta sauce}
{%
	\index{Spaghetti!Pasta sauce}%
	\st	In a \wok fry
		\ve{400}{g}{onions}{},
		\me{400}{g}{minced meat}{},
		\ve{3}{cloves}{garlic}{crushed}
		and
		\ve{100}{g}{mushrooms}{sliced}.
	\st	Stir in
		\gr{450}{g}{pasta sauce}{},
		and warm through.
	\st	\pasta{spaghetti}.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Potatoes American style}
{%
	\index{Style!American potatoes}%
	\st	In a \pan boil
		\ve{1500}{g}{potatoes}{sliced}
		and
		\ve{5}{}{spring onions}{chopped}
		in water with 
		\ch{2}{tsp}{ground turmeric}{}
		until potatoes done,
		then drain.
	\st	In a \wok fry
		\ve{200}{g}{onions}{chopped}
		and
		\ve{2}{cloves}{garlic}{crushed}
		in
		\ch{2}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ch{2}{tsp}{mixed herbs}{},
		\gr{400}{g}{canned tomatoes}{chopped}
		and simmer 5 minutes.
	\st	Stir in
		\da{150}{g}{tasty cheese}{grated}
		and
		\da{85}{ml}{cream}{},
		warm through,
		then pour over the potatoes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Egg and chips}
{%
	\st	Heat up
		\gr{800}{g}{oven ready chips}{}.
	\st	In a \wok fry
		\da{4}{}{eggs}{}
		in
		\ch{1}{tbsp}{oil}{}.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Chicken pilaf}%
{%
	\st	In a \wok fry
		\me{600}{g}{chicken}{},
		\ve{200}{g}{onions}{chopped}
		and 
		\ve{5}{cloves}{garlic}{crushed}
		in
		\ch{4}{tbsp}{oil}{}
		until chicken done.
	\st	Stir in
		\ch{1}{tsp}{ground cumin}{},
		\ch{5}{cm}{cinnamon stick}{},
		and
		\ch{6}{}{cloves}{}
		and fry for 2 minutes.
	\st	Stir in
		\gr{400}{g}{rice}{},
		\ch{1}{}{stock cube}{crumbled}
		and 
		\wa{800}{ml}{water}{}
		and bake, covered \med 30 minutes.
	\st	Spinkle on
		\gr{100}{g}{flaked almonds}{}
		before serving.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Vegetable shepherds pie}%
{%
	\index{Shepherds Pie!Vegetable}%
	\st	In a \pan boil
		\ve{1000}{g}{potatoes}{cubed},
		then mash with
		\da{50}{g}{butter}{}
		and
		\da{4}{tbsp}{milk}{}.
	\st	In a \cass mix
		\ve{300}{g}{carrots}{sliced},
		\ve{300}{g}{parsnips}{sliced},
		\ve{300}{g}{swedes}{sliced},
		\gr{400}{g}{canned borlotti beans}{undrained},
		\gr{200}{g}{mayonaise}{}
		and
		\ch{165}{g}{horseraddish}{}.
		Spread the mashed potatoes on top,
		sprinkle with
		\ch{50}{g}{sunflower seeds}{}
		and
		bake \med 60 minutes.
}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Onion pizza}%
{%
	\index{Pizza!Onion}
	\st	In a \wok slowly fry
		\ve{1000}{g}{onions}{chopped}
		and
		\ve{2}{cloves}{garlic}{crushed}
		in
		\ch{3}{tbsp}{oil}{}
		until brown.
	\st	Spread on
		\gr{4*9}{inch}{pizza bases}{}
		then sprinkle with
		\gr{200}{g}{pitted olives}{},
		\gr{100}{g}{anchovy fillets}{}
		and
		\ch{1}{tsp}{mixed herbs}{}.
		Bake \hi 20 minutes. 
}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Pasta and pesto}%
{%
	\st	\halfpasta{pasta whirls}.
	\st	Stir in 
		\gr{100}{g}{pesto}{} and
		\gr{150}{g}{canned tuna fish}{}.
}
\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Aubergine risotto}%
{%
	\index{Risotto!Aubergine}
	\st   In a \wok fry
		\ve{500}{g}{aubergine}{cubed},
		\ve{200}{g}{onion}{chopped}
		in
		\ch{2}{tbsp}{oil}{}
		until onions soft.
	\st	Stir in
		\ve{250}{g}{parsnips}{cubed},
		\gr{75}{ml}{sherry}{},
		\ve{150}{g}{tomatoes}{chopped},
		\ch{1}{}{stock cube}{crumbled},
		\gr{2}{tbsp}{grated parmesan}{},
		\gr{400}{g}{rice}{}
		and
		\wa{750}{ml}{water}{}.
		Bring to a boil and simmer until rice done.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Beans and bulgar wheat}
{%
	\st	In a \wok fry
		\ve{200}{g}{onions}{chopped},
		\ve{150}{g}{green peppers}{chopped},
		\ve{400}{g}{carrots}{sliced},
		\ve{4}{cloves}{garlic}{crushed},
		\ve{250}{g}{celery}{chopped}
		in
		\ch{2}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\gr{150}{g}{bulgar wheat}{},
		\gr{400}{g}{canned tomatoes}{chopped},
		\gr{150}{g}{tomato puree}{},
		\ch{1}{tsp}{chilli powder}{},
		\gr{2*400}{g}{canned red beans}{undrained},
		\ve{400}{g}{broccoli}{},
		\ch{1}{}{stock cube}{crumbled}
		and
		\wa{400}{ml}{water}{}
		and warm through.
	\st	Put it all in a \cass
		and bake \med 30 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Lamb hotpot}%
{%
	\st	In a \wok fry
		\me{400}{g}{lamb}{sliced}
		in it's own fat until done.
	\st	Stir in
		\ve{400}{g}{carrots}{chopped}
		and
		\ve{350}{g}{onions}{chopped}
		and fry until soft.
	\st	Stir in
		\ch{1}{}{bay leaf}{},
		\ch{1}{tsp}{thyme}{},
		\ch{1}{tbsp}{flour}{},
		\wa{600}{ml}{water}{}
		and
		\ch{2}{tbsp}{worcester sauce}{}.
		Put in a \cass and
		layer \ve{1500}{g}{potatoes}{sliced} on top.
		Bake covered \med 30 minutes,
		then uncovered 30 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Cheese and tagliatelli}%
{%
	\st	\halfpasta{tagliatelli}.
	\st	Stir in
		\da{100}{ml}{single cream}{},
		\gr{25}{g}{grated parmesan}{},
		\da{25}{g}{gruyere}{chopped},
		\da{25}{g}{stilton}{chopped}
		and gently warm until the cheese melts.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Tofu and mangetous stew}
{%
	\index{Stew!Tofu and mangetous}
	\st   \rice.
	\st   In a \wok fry
		\gr{300}{g}{firm tofu}{cubed}
		in
		\ch{7}{tbsp}{oil}{}
		until brown, then remove.
	\st	Fry \ve{200}{g}{onion}{sliced} until soft.
	\st	Stir in
		\ve{200}{g}{mangetout}{halved}
		and
		\ve{150}{g}{red peppers}{sliced},
		\ve{200}{g}{mushrooms}{sliced},
		\ve{400}{g}{cabbage}{sliced},
		\ch{3}{tbsp}{sherry}{},
		\ve{3}{cm}{ginger}{chopped},
		\ve{4}{cloves}{garlic}{crushed}
		and
		\ch{3}{tbsp}{soya sauce}{}
		and cook until done.
	\st	Return the tofu.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Vegetable cous cous}
{%
	\st	In a \wok fry
		\ve{200}{g}{onions}{chopped},
		\ve{225}{g}{courgettes}{sliced},
		\ve{225}{g}{green beans}{chopped},
		\ve{225}{g}{carrots}{chopped},
		\ve{500}{g}{cauliflower}{}
		and
		\ve{2}{cloves}{garlic}{crushed}
		in
		\ch{4}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ch{1}{tsp}{ground turmeric}{},
		\ch{1}{tsp}{ground cinamon}{},
		\ch{1}{}{stock cube}{crumbled},
		\gr{400}{g}{canned chickpeas}{drained}.
		and
		\wa{400}{ml}{water}{},
		and bring to the boil.
	\st	Make a space in the middle and pour in
		\gr{400}{g}{cous cous}{}
		in the middle, cover,
		and leave to stand for 10 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Charred aubergine and potato curry}
{%
	\index{Curry!charred aubergine and potato}
	\st	In a \pan boil
		\ve{1000}{g}{potatoes}{chopped}
		until done.
	\st	Grill or char
		\ve{800}{g}{aubergines}{}
		until burnt all over,
		peel and chop.
	\st	In a \wok in
		\ch{3}{tbsp}{oil}{}
		heat
		\ch{2}{tsp}{ground cumin}{}
		and
		\ch{2}{tsp}{mustard seeds}{}
		until the seeds pop.
	\st	Stir in
		\ve{400}{g}{onions}{chopped},
		\ve{4}{cm}{ginger}{chopped},
		\ve{1}{red}{chilli}{chopped},
		\ve{4}{cloves}{garlic}{crushed}
		and
		\ch{2}{tsp}{ground turmeric}{}
		and fry until the onions are soft.
	\st	Stir in 
		the potatoes,
		the aubergines,
		\ve{400}{g}{tomatoes}{chopped}
		and
		\wa{200}{ml}{water}{}
		cook until done.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Noodles and sardines}
{%
	\st	\halfnoodles.
	\st	Stir in
		\gr{120}{g}{canned sardines}{mashed}
		and
		\ch{1}{dsp}{soya sauce}{}.
}%
\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{End of Winter}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Spinach lasagna}% from Usenet
{%
	\index{Lasagna!Spinach}%
	\st	In a \wok in
		\ch{4}{tbsp}{oil}{}
		fry
		\ve{4}{cloves}{garlic}{crushed}
		and
		\ve{400}{g}{onions}{chopped}
		until soft.
	\st	Stir in
		\gr{400}{g}{canned tomatoes}{chopped},
		\gr{400}{ml}{passata}{},
		\ve{400}{g}{brocholi}{chopped},
		\gr{200}{g}{olives}{}
		and
		\ve{200}{g}{mushrooms}{}
		and cook until mushrooms are done.
	\st	In a \bowl mix	
		\gr{1}{tbsp}{grated parmesan}{},
		\da{250}{g}{cheddar cheese}{grated},
		\da{250}{g}{cottage cheese}{},
		\da{2}{}{eggs}{beaten}
		and
		\ve{250}{g}{spinach}{hacked}.
	\st	In a \cass layer
		\gr{200}{g}{lasagna}{}
		with the tomatoes and cheese 3 times.
		Bake \med 50 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Tofu and tahini}% from Vegan Health Plan
{%
	\st	In a \wok fry
		\ve{400}{g}{onions}{chopped},
		\ve{2}{cloves}{garlic}{crushed},
		\ve{150}{g}{green peppers}{chopped}
		and
		\ve{200}{g}{celery}{chopped}
		in
		\ch{4}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ch{1}{}{stock cube}{crumbled},
		\ch{1}{tbsp}{soy sauce}{},
		\gr{4}{tbsp}{tahini}{},
		\ch{1}{tsp}{ground nutmeg}{},
		\ch{2}{tsp}{miso}{},
		\ve{400}{g}{cooking apples}{chopped},
		\gr{100}{g}{canned pineapple}{chopped}
		and
		\wa{500}{ml}{water}{}
		and simmer for 10 minutes.
	\st	Put in a \cass
		and spinkle on top
		\gr{300}{g}{firm tofu}{cubed}
		and bake \med for 40 minutes.
	\st	\spud.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Chickpeas and tomatoes}
{%
	\st	In a \wok fry
		\ve{400}{g}{onions}{chopped}
		and
		\ve{4}{cloves}{garlic}{crushed}
		in
		\ch{2}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ve{2}{}{green chillis}{chopped},
		\ch{1}{tsp}{ground turmeric}{},
		\ch{1}{tsp}{paprika}{},
		\ch{1}{tbsp}{ground cumin}{},
		\ch{1}{tbsp}{ground coriander}{},
		\ch{1}{tsp}{garam masala}{}
		and fry for 1 minute.
	\st	Stir in
		\gr{400}{g}{canned tomatoes}{chopped}
		and
		\gr{400}{g}{canned chickpeas}{undrained}
		and simmer for 20 minutes.
	\st	\yellowrice.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Curry and couscous}%
{%
	\st	In a \pan warm
		\gr{400}{g}{canned curry}{}.
	\st	\halfcouscous.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Pasta and bacon in white sauce}% from Alan and Paul
{%
	\st	\pasta{pasta shells}.
	\st	In a \wok fry
		\ve{350}{g}{onions}{chopped},
		\ve{200}{g}{celery}{chopped},
		\ve{150}{g}{red peppers}{chopped},
		\ve{200}{g}{mushrooms}{sliced}
		and
		\me{100}{g}{bacon}{chopped}
		in
		\ch{2}{tbsp}{oil}{}
		until onions soft.
	\st	Stir in
		\ch{2}{tbsp}{flour}{}
		until completely absorbed.
	\st	Stir in
		\gr{400}{ml}{UHT milk}{}
		and stir
		until sauce thickens.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Seaweed Hash}% David Carr
{%

	\item	In a \pan boil
		\ve{1000}{g}{potatoes}{diced}
		until done,
		then drain.
	\item	In a \wok heat
		\ch{3}{tbsp}{oil}{}
		and
		\ch{1}{tbsp}{mustard seeds}{}
		until they start to pop.
	\item	Stir in
		\ve{300}{g}{red peppers}{sliced},
		\ve{300}{g}{mushrooms}{},
		\ve{250}{g}{seaweed}{chopped}
		and
		\ve{400}{g}{onions}{chopped}
		and fry until done.
	\item	Stir in the potatoes
		and warm through.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Spiced chicken}%
{%
	\st	\orangerice.
	\st	In a \cass mix
		\me{600}{g}{chicken}{pieces},
		\ve{2}{cloves}{garlic}{crushed},
		\ve{4}{cm}{ginger}{chopped},
		\ch{2}{tsp}{ground turmeric}{} and
		\ch{2}{tbsp}{oil}{}
		and
		bake \med 20 minutes.
	\st	In a \wok fry
		\ve{400}{g}{onions}{chopped}{},
		\ve{150}{g}{green peppers}{chopped}
		in
		\ch{2}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ch{1}{tsp}{ground cumin}{},
		\ch{1}{tsp}{ground coriander}{}, 
		\ve{2}{}{red chillis}{finely chopped}
		and
		\ch{1}{}{bay leaf}{crumbled}
		and fry for 1 minute.
	\st	Take off heat
		and
		stir in
		\da{150}{g}{natural yoghurt}{}
		and
		\wa{55}{ml}{water}{warm}.
		Pour over the chicken
		and bake,
		covered \med for 10 minutes.
}%
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Pasta and stir in sauce}%
{%
	\st	\halfpasta{tagliatelli}.
	\st	Stir in
		\gr{150}{g}{ready made pasta sauce}{}.
}%

\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\season{Spring}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{Beginning of Spring}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Bean and potato stew}% Oxfam Provencal Bean Casserole
{%
	\index{Stew!Bean and potato}%
	\st	\spud.
	\st	In a \wok fry
		\ve{4}{}{cloves garlic}{crushed},
		\ve{400}{g}{onions}{sliced}
		and
		\ve{150}{g}{red peppers}{sliced}
		in
		\ch{5}{tbsp}{oil}{}
		until soft.
	\st	Stir in	
		\ve{400}{g}{aubergine}{sliced},
		\ve{600}{g}{mushrooms}{sliced},
		\ve{1000}{g}{courgettes}{sliced},
		\gr{300}{g}{canned tomatoes}{chopped}
		and
		\gr{300}{g}{canned flageolot beans}{}{}
		simmer for 20 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Chicken and carrot stew}%
{%
	\index{Stew!Chicken and carrot}
	\st	In a \wok mix
		\me{400}{g}{chicken}{cubed},
		\ve{400}{g}{onions}{chopped},
		\ch{2}{tsp}{ground ginger}{},
		\ch{1}{tsp}{ground cinnamon}{},
		\ve{1}{clove}{garlic}{crushed},
		\ch{2}{}{stock cubes}{crumbled},
		\ve{1000}{g}{carrots}{sliced},
		\ch{1}{tbsp}{honey}{},
		\ve{3}{tsp}{mixed herbs}{},
		\ch{3}{tp}{ground coriander}{},
		\ch{3}{tbsp}{oil}{},
		and
		\wa{800}{ml}{water}{}.
		Bring to the boil
		then simmer, uncovered for 60 minutes.
	\st	\couscous.
	\st	Stir in the juice of
		\ve{1}{}{lemon}{}
		to the stew 
		before serving.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Curry Ethiopian style}
{
	\index{Style!Ethiopian curry}%
	\index{Curry!Ethiopian}
	\st	\rice.
	\st	In a \wok fry
		\ve{200}{g}{onions}{chopped}
		and
		\ve{2}{cloves}{garlic}{crushed}
		in
		\ch{2}{tbsp}{oil}{}
		until brown.
	\st	Stir in
		\ch{1}{tsp}{paprika}{},
		\ch{2}{tbsp}{curry powder}{},
		\gr{300}{g}{red lentils}{}
		and
		\wa{1000}{ml}{water}{}
		and simmer for 30 minutes.
	\st	Stir in
		\ch{2}{tbsp}{wine vinegar}{}
		and simmer for 5 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Tagliatelli and bacon}%
{%
	\st	\halfpasta{tagliatelli}.
	\st	In a \wok fry
		\me{50}{g}{bacon}{chopped}
		without oil until brown.
	\st	Stir in
		\da{100}{ml}{double cream}{},
		warm
		and
		then add the drained pasta.
	\st	Warm and sprinkle with
		\gr{50}{g}{grated parmesan}{}.
}%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Tofu and pork}
{%
	\st	In a \wok fry
		\me{200}{g}{minced pork}{},
		\ve{2}{}{red chillis}{chopped}
		and
		\ve{4}{cm}{ginger}{chopped}
	      	in
      		\ch{2}{tbsp}{oil}{}
	      	until the pork is done.
	\st	Stir in
		\ch{2}{tbsp}{flour}{},
     		\ch{1}{}{stock cube}{crumbled},
      		\ch{1}{tbsp}{sherry}{},
		\ve{400}{g}{mange tout}{halved},
		\wa{250}{ml}{water}{},
		bring to boil
		and
		simmer for 10 minutes.
	\st	Stir in
		\gr{450}{g}{tofu}{cubed},
		and
		simmer for 10 minutes.
	\st	\noodles.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Vegetable and butter bean pie}%
{%
	\index{Pie!Vegetable and butter bean}
	\st	\spud.
	\st	In a \wok fry
		\ve{200}{g}{onions}{chopped},
		\ve{400}{g}{carrots}{sliced},
		\ve{400}{g}{leeks}{sliced},
		\ve{150}{g}{mushrooms}{sliced}
		in
		\ch{3}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\gr{400}{g}{canned butter beans}{drained},
		\gr{400}{g}{canned tomatoes}{choppped},
		\ch{1}{tsp}{mixed herbs}{},
		\ch{1}{tbsp}{flour}{},
		\ch{1}{}{stock cube}{crumbled}
		and
		\wa{2}{tbsp}{water}{}
		and warm through.
	\st	Put in a \cass
		and
		cover with
		\gr{1}{pack}{flakey pastry}{rolled}
		and
		bake \med for 30 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Coconut chickpeas}%
{%
	\st	\rice.
	\st	In a \wok fry
		\ve{200}{g}{onions}{chopped}
		in
		\ch{2}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\gr{400}{g}{canned chickpeas}{undrained} (mashed),
		\ve{300}{g}{tomatoes}{chopped},
		\ch{1}{tsp}{ground coriander}{},
		\ch{2}{tsp}{ground turmeric}{},
		\ch{50}{g}{creamed coconut}{crumbled}
		and 
		\ch{1}{tsp}{chilli powder}{}
		and simmer for 10 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Oven ready pizza}%
{%
	\st	Bake
		\gr{2*9}{inch}{ready made pizzas}{}
		\hi for 20 minutes or until golden.
}%

\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Meat and potatoes Mexican style}% Betty Crowshaw
{%
	\index{Style!Mexican meat and potatoes}%
	\st	In a \wok mix
		\me{400}{g}{minced meat}{},
		\ve{400}{g}{onions}{chopped}
		\ve{150}{g}{red peppers}{chopped}
		and
		\ve{1}{clove}{garlic}{crushed}
		and fry until done.
	\st	Stir in
		\gr{400}{g}{canned tomatoes}{chopped},
		\gr{200}{g}{canned sweetcorn}{drained},
		\ch{1}{tbsp}{honey}{}
		and
		\ch{2}{}{red chillis}{chopped}.
	\st	Put in a \cass
		and cover with a layer of
		\ve{1000}{g}{potatoes}{sliced}
		and sprinkle with
		\da{50}{g}{cheese}{grated}.
		Cover and bake \med for 50 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Turnip and chickpea stew}%
{%
	\index{Stew!Turnip and chickpea}
	\st	In a \pan mix
		\ve{750}{g}{turnips}{cubed},
		\ve{200}{g}{onions}{chopped},
		\gr{400}{g}{canned chick peas}{drained},
		\ch{1}{tbsp}{honey}{},
		\ch{0.5}{tsp}{ground cinnamon}{},
		\ch{1}{tsp}{ground coriander}{}
		\ch{1}{tsp}{ground cumin}{},
		\ch{1}{tsp}{ground ginger}{}
		and
		\ch{2}{tbsp}{oil}{},
		cover with water,
		and simmer uncovered for 60 minutes.
	\st	\couscous.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Cashew curry}%
{%
	\index{Curry!Cashew}
	\st	\rice.
	\st	In a \wok fry
		\ve{400}{g}{onions}{sliced}
		and
		\ve{3}{cloves}{garlic}{crushed}
		in
		\ch{3}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ch{1}{tbsp}{curry powder}{}
		and
		\gr{250}{g}{cashews}{}
		and simmer for 5 minutes.
	\st	Stir in
		\gr{100}{g}{creamed coconut}{crumbled}
		and
		\wa{200}{ml}{water}{}
		and simmer for 10 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Scrambled eggs}%
{%
	\st	In a \wok fry
		\ve{150}{g}{red peppers}{sliced}
		in
		\ch{1}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\da{4}{}{eggs}{beaten},
		\da{4}{tbsp}{milk}{}
		and warm until firm.
	\st	Serve in
		\gr{4}{}{pitta}{warmed}.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Kedgeree}%
{%
	\st	\rice.
	\st	Stir in
		\me{400}{g}{kippers}{chopped},
		\da{25}{g}{butter}{},
		\ch{1}{tsp}{mustard}{},
		\da{4}{}{eggs}{soft boiled}
		and
		\ch{0.5}{tsp}{chilli powder}{}.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Chilli bean stew}%
{%
	\st	In a \wok fry
		\ve{400}{g}{onions}{sliced}
		and
		\ve{4}{cloves}{garlic}{crushed}
		in
		\ch{2}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ve{250}{g}{celery}{chopped}
		and
		\ve{150}{g}{red peppers}{chopped}
		and
		cook for 5 minutes.
	\st	Stir in
		\gr{400}{g}{canned tomatoes}{chopped},
		\gr{400}{g}{canned red beans}{},
		\gr{75}{g}{tomato puree}{},
		\ve{1}{}{green chilli}{chopped},
		\ch{1}{cube}{stock}{crumbled}
		and
		\wa{7}{tbsp}{water}{}.
		and simmer for 5 minutes.
	\st	Put in a \cass and layer with
		\ve{1000}{g}{potatoes}{sliced}
		Sprinkle with
		\da{200}{g}{cheddar cheese}{grated}.
		and bake \med for 60 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Vegetables and pasta}% Vegan health plan
{%
	\st	\pasta{pasta twists}.
	\st	In a \wok fry
		\ve{200}{g}{onions}{chopped}
		and
		\ve{250}{g}{celery}{chopped},
		in
		\ch{3}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ve{150}{g}{red peppers}{chopped},
		\ve{400}{g}{courgettes}{sliced},
		\ve{4}{cloves}{garlic}{crushed},
		\ve{100}{g}{mushrooms}{chopped}
		and
		\gr{200}{g}{canned sweetcorn}{}
		and warm through.
	\st	Stir in
		\ch{1}{tbsp}{flour}{}.
	\st	Remove from heat and stir in
		\da{500}{ml}{milk}{}
		until a sauce is formed.
	\st	Stir in
		the pasta,
		\ch{1}{tsp}{dried parsley}{},
		\ch{1}{tbsp}{soya sauce}{}
		\ch{2}{tsp}{ground coriander}{}
		and
		\ch{2}{tsp}{miso}{}
		and warm through.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Fish fingers and baked beans}
{%
	\st	In a \pan heat up
		\gr{400}{g}{canned baked beans}{}.
	\st	Grill
		\gr{8}{}{fish fingers}{}.
}%
\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{Spring Equinox}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Potato and cheese bake}%
{%
	\st	In a \pan boil
		\ve{2000}{g}{potatoes}{sliced}
		for 15 minutes,
		then drain.
	\st	In a \wok fry
		\ve{800}{g}{onions}{sliced}
		and
		\me{200}{g}{bacon}{chopped}
		in
		\ch{4}{tbsp}{oil}{}
		until bacon done.
	\st	Layer the potatoes, onions and
		\da{400}{g}{cheese}{grated}
		in a \cass
		then bake \med for 30 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Peanut butter and black eyed bean stew}%
{%
	\st	\rice.
	\st	In a \wok,
		fry, in \ch{2}{tbsp}{oil}{}
		\ve{200}{g}{onion}{chopped}
		until soft.
	\st	Stir in
		\ch{2}{tbsp}{flour}{},
		\gr{400}{g}{canned black eyed beans}{undrained},
		\gr{2}{tbsp}{peanut butter}{}
		and simmer for 5 minutes.
	\st	Stir in
		\ve{4}{}{tomatoes}{chopped}
		the juice of
		\ve{1}{}{lemon}{},
		and
		simmer for 15 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Vegetable crumble}%
{%
	\st	In a \wok fry
		\ve{400}{g}{onions}{chopped},
		\ve{4}{cloves}{garlic}{crushed}
		in
		\ch{3}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ch{3}{tsp}{miso}{},
		\ch{1}{}{stock cube}{crumbled},
		\wa{300}{ml}{water}{},
		\ve{1000}{g}{potatoes}{chopped},
		\ve{500}{g}{parsnips}{chopped},
		\ve{500}{g}{carrots}{chopped}
		and
		\gr{400}{g}{canned tomatoes}{chopped}
		then put in a \cass.
	\st	In a \bowl mix
		\ch{300}{g}{flour}{},
		\da{150}{g}{margarine}{},
		\ch{100}{g}{chopped nuts}{},
		and
		\ch{100}{g}{sunflower seeds}{}
		and layer on top of \cass,
		then bake \med for 60 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Tagliatelli and mushrooms}%
{%
	\st	\halfpasta{tagliatelli}.
	\st	In a \wok fry
		\ve{150}{g}{onion}{chopped}
		without oil until soft.
	\st	Stir in
		\ve{150}{g}{mushrooms}{chopped}
		and
		fry until soft.
	\st	Stir in
		\da{100}{ml}{double cream}{},
		warm
		and
		then add the drained pasta.
	\st	Warm and sprinkle with
		\gr{50}{g}{grated parmesan}{}.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Groundnut stew}%
{%
	\st	In a \pan stew
		\ve{1000}{g}{potatoes}{},
		\ve{500}{g}{carrots}{},
		\ve{400}{g}{swede}{chopped},
		\ve{200}{g}{yams}{chopped},
		\ve{200}{g}{sweet potatoes}{chopped},
		\ve{200}{g}{onions}{mashed},
		\ve{2}{cloves}{garlic}{mashed},
		\ve{4}{cm}{ginger}{chopped},
		\ve{2}{}{tomatoes}{chopped},
		\gr{2}{tbsp}{peanut butter}{},
		\ch{1}{}{stock cube}{crumbled},
		\gr{1}{tsp}{chilli powder}{}
		and
		\wa{400}{ml}{water}{}.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Tuna and rice}%
{%
	\st	\rice.
	\st	In a \wok fry
		\ve{400}{g}{onions}{chopped}
		\ve{150}{g}{red peppers}{chopped},
		and
		\ve{150}{g}{green peppers}{chopped}
		until done.
	\st	Stir in
		\gr{150}{g}{canned tuna fish}{}
		and the rice.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Green lentil lasagne}
{%
	\st	\spud.
	\st	In a \pan cook 
		\gr{200}{g}{green lentils}{}
		until soft.
		Save 200 ml of the water.
	\st	In a \wok fry
		\ve{200}{g}{onion}{sliced},
		\ve{2}{cloves}{garlic}{crushed}
		and
		\ve{200}{g}{mushrooms}{sliced}
		in
		\ch{3}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\da{500}{ml}{milk}{},
		\ch{2}{tbsp}{flour}{},
		\ch{1}{}{bay leaf}{crumbled},
		\ch{1}{tsp}{ground nutmeg}{}
		and 
		\ch{2}{tsp}{ground coriander}{}
		until sauce thinkens.
	\st	Stir in
		the lentils
		and
		the water.
	\st	Layer with
		\gr{450}{g}{lasagne}{}
		and bake \med for 50 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{bacon, smash and cheese}%
{%
	\st	In a \wok fry
		\me{100}{g}{bacon}{chopped}.
	\st	In a \pan mix
		\gr{175}{g}{smash}{}
		and
		\wa{800}{ml}{water}{boiling}.
	\st	Stir in
		\da{100}{g}{cheese}{grated}
		and
		the bacon.
}%

\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Vegetable pizza}%
{%
	\index{Pizza!Vegetable}%
	\st	In a \wok fry
		\ve{200}{g}{carrots}{chopped},
		\ve{200}{g}{leeks}{chopped}
		and
		\ve{250}{g}{courgettes}{chopped}
		in
		\ch{2}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\gr{75}{g}{tomato puree}{}
		and warm through.
	\st	Layer on
		\gr{4*9}{inch}{pizza bases}{}
		and
		\da{50}{g}{mature cheese}{grated}
		and bake \med for 20 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Gammon rice}% BBC Good Food
{%
	\st	In a \pan fry in
		\ch{1}{tbsp}{oil}{},
		\ve{3}{}{onions}{}
		until soft.
	\st	Stir in
		\me{225}{g}{smoked gammon}{shredded}
		and cook until brown.
	\st	Stir in
		\gr{350}{g}{rice}{},
		\ch{1}{}{stock cube}{},
		\wa{900}{ml}{water}{},
		\gr{400}{g}{canned sweetcorn}{},
		\ch{1}{tsp}{ground turmeric}{},
		boil,
		then simmer for 15 minutes.
	\st	Stir in
		\gr{175}{g}{frozen peas}{}
		and simmer for 5 minutes.
	\st	In a dry \wok roast
		\gr{50}{g}{unsalted peanuts}{}
		until brown,
		and sprinkle on top.
}%
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Tomato tofu}% From Karen Turvey
{%
	\st	In a \wok fry
		\ve{400}{g}{onions}{chopped},
		\ve{200}{g}{carrots}{chopped},
		\ve{2}{cloves}{garlic}{crushed},
		\ve{150}{g}{red peppers}{chopped}
		and
		\ve{100}{g}{mushrooms}{chopped}
		in
		 \ch{3}{tbsp}{vegetable oil}{}
		until the mushrooms are done.
	\st	Stir in
		\gr{150}{g}{tomato puree}{},
		\ch{2}{tbsp}{soya sauce}{}
		and
		\gr{400}{g}{canned tomatoes}{}
		and simmer for 10 minutes.
		\st Spinkle on 
		\gr{450}{g}{tofu}{cubed},
		cover and simmer for 10 minutes.
	\st	\couscous.
}% 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Tagliatelle and cheese}% David Carr
{%
	\st	\halfpasta{tagliatelli}.
	\st	In a \wok fry
		\ve{2}{cloves}{garlic}{crushed}
		and
		\ve{150}{g}{green peppers}{chopped}
		until soft, 
		then mash.
	\st	Stir in
		\da{200}{g}{cottage cheese}{},
		\da{200}{g}{gorgonzola}{grated}
		and
		\ch{50}{g}{grated parmesan}{}
		and warm.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Potato and onion pie}%
{%
	\index{Pie!Potato and onion}
	\st	In a \cass mix
		\ve{1500}{g}{potatoes}{chopped},
		\ve{500}{g}{onions}{chopped},
		\ve{4}{cloves}{garlic}{crushed},
		\da{400}{g}{tasty cheese}{},
		\ch{2}{tbsp}{whole grain mustard}{}
		and
		cover with		
		\gr{1}{pack}{ready made pastry}{}.
		Then bake 60 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Spaghetti bolognese}% Sue Pennington
{%
	\st	In a \wok fry
		\me{200}{g}{minced meat}{}
		\me{100}{g}{bacon}{chopped}
		\ve{200}{g}{onions}{chopped},
		\ve{200}{g}{leeks}{chopped}
		until the meat is done.
	\st	Stir in
		\ch{1}{cube}{stock}{crumbled},
		\ch{1}{tsp}{oregano}{},
		\ve{200}{g}{tomatoes}{chopped},
		\gr{400}{g}{canned tomatoes}{chopped}
		\gr{75}{g}{tomato puree}{}
		\ve{150}{g}{red peppers}{chopped},
		\ve{150}{g}{green peppers}{chopped},
		\ve{200}{g}{carrots}{chopped}
		\ve{250}{g}{courgettes}{chopped}
		simmer 40 minutes.
	\st	\pasta{spaghetti}.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Pepper risotto}%
{%
	\index{Risotto!Pepper}
	\st	In a \wok fry
		\ve{1}{}{red chilli}{chopped},
		\ve{150}{g}{red peppers}{chopped},
		\ve{150}{g}{green peppers}{chopped},
		\ve{400}{g}{onion}{chopped}
		in
		\ch{2}{tbsp}{oil}{}
		until onions soft.
	\st	Stir in
		\ch{75}{ml}{sherry}{},
		\ve{150}{g}{tomatoes}{chopped},
		\ch{1}{}{stock cube}{crumbled},
		\gr{2}{tbsp}{grated parmesan}{},
		\gr{400}{g}{rice}{}
		and
		\wa{750}{ml}{water}{}.
		Bring to a boil and stand until rice done.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Sweet corn and bacon}%
{%
	\st	In a \pan boil
		\da{2}{}{eggs}{}
	\st	In a \wok fry
		\me{100}{g}{bacon}{chopped}
		in
		\ch{2}{tbsp}{oil}{}
		until done.
	\st	Stir in
		\ch{2}{tbsp}{flour}{}
		until absorbed.
	\st	Stir in the liquid from
		\gr{2*400}{g}{canned sweet corn}{}
		and
		\da{600}{ml}{milk}{}.
	\st	Add the eggs (halved).
}%

\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Cashew and pea curry}
{%
	\index{Curry!Cashew and pea}%
	\st	\rice.
	\st	In a \bowl blend
		\ch{5}{}{cloves}{},
		\ch{1}{tbsp}{curry powder}{},
		\ve{4}{cm}{ginger}{chopped},
		\gr{2}{tbsp}{chopped cashew nuts}{},
		\ch{2}{tbsp}{poppy seeds}{},
		\wa{150}{ml}{water}{}
		and 
		\ve{1}{}{green chilli}{chopped}. 
	\st	In a \wok fry
		\ve{200}{g}{onions}{chopped},
		and
		\ve{2}{cloves}{garlic}{crushed}
		in
		\ch{3}{tbsp}{oil}{}
		until soft.
	\st	Stir in the blended spices
		and
		\gr{1}{tbsp}{raisins}{}
		and warm through. 
	\st	Stir in
		\gr{110}{g}{frozen peas}{},
		\ve{100}{g}{mushrooms}{},
		\da{3}{tbsp}{cream}{},
		\da{4}{tbsp}{yoghurt}{}
		and 
		\wa{150}{ml}{water}{}
		and simmer for 5 minutes.
	\st	Sprinkle 
		\gr{2}{tbsp}{chopped cashew nuts}{}
		on top.
}%
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Meat and bean stew}
{%
	\index{Stew!Meat and bean}%
	\st	In a \wok in
		\ch{2}{tbsp}{oil}{}
		fry
		\ve{200}{g}{onions}{chopped},
		\ve{4}{cloves}{garlic}{crushed}
		and
		\me{400}{g}{minced meat}{}
		until meat is done.
	\st	Stir in
		\gr{400}{g}{canned kidney beans}{drained}
		\gr{400}{g}{canned lima beans}{drained},
		\gr{400}{g}{canned chickpeas}{drained},
		\ch{1}{tsp}{mustard}{},
		\gr{150}{g}{tomato puree}{},
		\ch{1}{tsp}{ground cumin}{}
		and
		\ch{half}{glass}{sherry}{}.
		Put in a \cass
		cover and bake \med for 60 minutes.
	\st	\spud.
}%
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Vegetable cous cous}% David Carr
{%
	\st	In a \wok in
		\ch{3}{tbsp}{olive oil}{}
		fry quickly
		\ve{300}{g}{onions}{chopped},
		\gr{400}{g}{canned chickpeas}{},
		\ve{300}{g}{potatoes}{chopped},
		\ve{300}{g}{turnips}{chopped},
		\ve{300}{g}{carrots}{chopped},
		\ve{300}{g}{courgettes}{chopped},
		\ve{150}{g}{green peppers}{chopped},
		\ve{3}{cloves}{garlic}{crushed}
		and
		\ve{1}{}{red chilli}{chopped} 
		until warm.
	\st	Stir in
		\ch{1}{cube}{stock}{crumbled},
		\ch{1}{tsp}{ground cumin}{},
		\ch{1}{tsp}{ground cinammon}{}
		and
		\wa{500}{ml}{water}{}
		and simmer until vegetables are done.

	\st	In a dry \wok toast
		\gr{400}{g}{cous cous}{}
		until it starts to change colour.
	\st	Stir in 
		\ch{1}{tsp}{ground turmeric}{},
		\ch{1}{cube}{stock}{crumbled},
		\ch{3}{tbsp}{olive oil}{},
		\gr{75}{g}{raisins}{}
		and 
		\gr{75}{g}{apricots}{chopped}
		then put in a \cass.
	\st	Pour on
		\wa{800}{ml}{water}{boiling},
		cover and leave to stand for 20 minutes.
	\st	Top the cous cous with the vegetables.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Cheesey beans in pitta}%
{%
	\st	\gr{400}{g}{baked beans}{},
		\gr{4}{}{pitta bread}{warmed}
		and
		\da{50}{g}{mature cheese}{grated}.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Carrot and parsnip curry}%
{%
	\index{Curry!Carrot and parsnip}%
	\st	\rice.
	\st	In a \wok fry
		\ve{2}{cloves}{garlic}{crushed},
		\ve{200}{g}{onions}{chopped}
		and
		\ve{1}{}{green chilli}{chopped}
		in
		\ch{4}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ve{250}{g}{cauliflower}{flourettes},
		\ve{350}{g}{carrots}{sliced}
		and
		\ve{300}{g}{parsnips}{chopped}
		and simmer until soft.
	\st	Stir in
		\ch{2}{tbsp}{curry powder}{},
		\ch{1}{tsp}{ground turmeric}{}
		and
		\ve{4}{cm}{ginger}{chopped}
		and 
		cook for 2 minutes.
	\st	Stir in
		\da{300}{ml}{greek yoghurt}{},
		\wa{200}{ml}{water}{}
		and
		\gr{50}{g}{ground almonds}{}
		and warm through.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Courgette tagliatelli}% David Carr
{%
	\st	In a \wok in
		\ch{2}{tbsp}{oil}{}
		slowly fry
		\ve{200}{g}{onions}{chopped}
		until done.
	\st	Stir in
		\ve{400}{g}{courgettes}{sliced}
		and cook slowly for 
		60 minutes.
	\st	\pasta{tagliatelli}.
	\st	Mash the courgettes and then
		stir in
		\gr{400}{g}{frozen peas}{}
		and warm through.
	\st	Sprinkle with
		\gr{50}{g}{grated parmesan}{}
		before serving.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Tarka dhal and chappatis}% David Carr
{%
	\index{Curry!Tarka dhal and chappatis}%
	\st	In a \pan cook
		\ch{1}{}{bay leaf}{},
		\ch{1}{tbsp}{curry powder}{},
		\ch{1}{tsp}{ground turmeric}{}
		and
		\gr{225}{g}{red lentils}{},
		in
		\wa{450}{ml}{water}{}
		until soft.
	\st	In a \wok in
		\ch{3}{tbsp}{oil}{}
		fry
		\ch{1}{tsp}{cumin seeds}{}
		and
		\ch{1}{tsp}{mustard seeds}{}
		until mustard seeds pop.
	\st	Stir in
		\ve{200}{g}{onions}{sliced},
		\ve{2}{cloves}{garlic}{crushed},
		\ve{4}{cm}{ginger}{chopped}
		and
		\ve{2}{}{green chillis}{chopped}
		and
		fry until onion browns.
	\st	Stir in the lentils
		and
		\ch{25}{g}{creamed coconut}{}
		and warm through.
	\st	Heat up
		\gr{8}{}{chappattis}{}
		before serving.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Muffin pizzas}%
{%
	\st	Grill
		\gr{8}{}{muffins}{}
		until brown.
	\st	Top with 
		\gr{75}{g}{tomato puree}{},
		\ve{100}{g}{mushrooms}{sliced},
		\gr{150}{g}{sweet corn}{},
		\gr{150}{g}{canned tuna fish}{}
		and
		\da{100}{g}{cheese}{grated}.
}%

\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{End of Spring}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Potato and bacon omelette}%
{%
	\st	In a \pan boil
		\ve{1200}{g}{potato}{sliced} then drain.
	\st	In a \wok fry
		\ve{350}{g}{onions}{chopped}
		and
		\me{150}{g}{bacon}{chopped}
		in
		\ch{2}{tbsp}{oil}{}.
	\st	Stir in the potatoes
		and
		\da{50}{g}{gruyere cheese}{grated}{}.
	\st	Stir in
		\da{4}{}{eggs}{beaten}
		and cook until nearly done.
	\st	Sprinkle on
		\da{50}{g}{cheddar cheese}{grated}{}
		and grill.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Chicken and cauliflower}% Judith Parry-Evans
{%
	\index{Curry!Chicken and cauliflower}
	\st	In a \cass bake
		\me{400}{g}{chicken pieces}{}
		until done.
	\st	Cover with 
		\ve{700}{g}{cauliflower}{flourettes}.
	\st	In a \bowl mix
		\gr{300}{g}{canned condensed chicken soup}{},
		\gr{200}{g}{mayonaise}{},
		\gr{0.5}{cup}{sherry}{},
		\ch{1}{tsp}{curry powder}{}
		and
		juice of
		\ve{1}{}{lemon}{}
		and pour over the cauliflower
		and bake \med for 30 minutes.
	\st	\rice.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Black eyed bean stew}%
{%
	\index{Stew!Black eyed bean}%
	\st	\noodles.
	\st	In a \wok fry
		\ve{1}{}{onion}{sliced}
		in 
		\da{25}{g}{butter}{}
		until soft.
	\st	Stir in
		\ve{2}{}{tomatoes}{chopped}
		and 
		simmer for 5 minutes.
	\st	Stir in
		\gr{225}{g}{black eyed beans}{mashed}
		\ve{1}{}{chilli}{chopped}
		and
		simmer for 10 minutes,
		add water if necessary.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Cheese and tomato omelette}%
{%
	\st	\da{4}{}{eggs}{beaten},
		\ve{6}{}{tomatoes}{chopped}
		and
		\da{50}{g}{mature cheese}{grated}.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Banana Curry}% David Carr
{%
	\index{Curry!Banana}
	\st	In a \wok fry
		\ve{400}{g}{onions}{chopped},
		\ve{2}{}{green chilli}{},
		\ve{8}{cm}{ginger}{chopped}
		in
		\ch{6}{tbsp}{oil}{}
		until onions soft.
	\st	Stir in
		\ch{1}{tbsp}{curry powder}{}
		and
		\ch{1}{tsp}{mustard seeds}{}
		until mustard starts to pop.
	\st	Stir in
		\ve{1000}{g}{green bananas}{chopped}
		and fry quickly until hot.
	\st	\rice.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Tofu and peppers}% David Carr
{%
	\st	\couscous.
	\st	In a \wok fry
		\ve{1}{}{red chilli}{chopped},
		\ve{1}{}{green chilli}{chopped},
		\ve{150}{g}{red peppers}{sliced},
		\ve{400}{g}{tomatoes}{chopped}
		in
		\ch{3}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\gr{300}{g}{tofu}{cubed},
		\gr{1}{tbsp}{blackbean sauce}{}
		and warm through.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Vegetable chilli stew}% David Carr
{%
	\index{Stew!Vegetable chilli}
	\st	In a \pan boil
		\ve{1000}{g}{potatoes}{chopped}
		until not quite done
		then drain and put in \cass.
	\st	In a \wok fry
		\ve{200}{g}{onions}{chopped},
		\ch{1}{}{stock cube}{crumbled},
		\ve{3}{cloves}{garlic}{},
		\ve{1}{}{red chilli}{chopped},
		\ve{1}{}{green chilli}{chopped},
		in
		\ch{4}{tbsp}{oil}{}
		for 5 minutes.
	\st	Stir in
		\ve{150}{g}{red peppers}{chopped},
		\ve{150}{g}{green peppers}{chopped},
		\gr{400}{g}{canned kidney beans}{drained},
		\gr{400}{g}{canned cannellini beans}{drained}
		and simmer 5 minutes.
	\st	Stir in
		\gr{400}{g}{canned tomatoes}{chopped},
		\gr{150}{g}{tomato puree}{},
		\gr{500}{g}{creamed tomatoes}{}
		and
		\gr{1}{glass}{sherry}{}
		and warm through.
	\st	Pour on top of the potatoes
		and bake 30 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Spaghetti and rocket}% David Carr
{%
	\st	\halfpasta{spaghetti}
	\st	Stir in
		\ve{200}{g}{rocket}{chopped}
		and
		\da{50}{g}{butter}{}.
	\st	Sprinkle on
		\ch{20}{g}{grated parmesan}{}.
}%

\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\season{Summer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{Beginning of Summer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Roasted vegetable pie}% Carnation can
{%
	\st	In a \cass mix
		\ve{300}{g}{onion}{chopped},
		\ve{150}{g}{red peppers}{},
		\ve{150}{g}{yellow pepper}{},
		and
		\ve{200}{g}{courgettes}{chopped},
		and bake \hi\ 25 minutes.
	\st	In a bowl mix
		\da{3}{}{eggs}{beaten},
		\da{100}{g}{feta cheese}{}
		and
		\gr{400}{g}{canned evapourated milk}{}.
		Pour over the vegetables,
		cover with
		\gr{1}{pack}{ready made pastry}{}
		and bake \med 40 minutes.		
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Liver and sausage casserole}% Janes slimming book
{%
	\st	In a \cass bake
		\me{125}{g}{sausages}{chopped}
		\med for 30 minutes.
	\st	In a \cass mix
		the sausages,
		\me{350}{g}{liver}{chopped},
		\ve{200}{g}{onions}{chopped},
		\gr{300}{g}{canned tomato soup}{},
		\ch{2}{tbsp}{worcestershire sauce}{},
		\ch{1}{tsp}{vinegar}{},
		\ch{1}{tsp}{mustard}{}
		and
		bake \med for 60 minutes.
	\st	\rice.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Fish chowder}% Usenet
{%
	\st	In a \pan in
		\wa{400}{ml}{water}{}
		boil
		\ve{1000}{g}{potatoes}{cubed}
		for 10 minutes.
	\st	Stir in
		\me{300}{g}{fish}{chopped}
		and
		\gr{400}{g}{sweet corn}{}
		and simmer for 10 minutes.
	\st	In a \wok fry
		\me{100}{g}{bacon}{}
		and
		\ve{500}{g}{onions}{chopped}
		until bacon done.
	\st	Stir in
		\ch{2}{tbsp}{flour}{}
		until absorbed
		and then stir in
		\da{500}{ml}{milk}{}
		to make a sauce.
	\st	Mix the fish and the bacon
		mixtures together.
}%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Spam and mustard pasta}% Judith Parry-Evans
{%
	\st	\halfpasta{pasta shells}.
	\st	In a \wok in
		\ch{2}{tbsp}{oil}{}
		fry
		\gr{200}{g}{spam}{sliced},
		\ve{3}{cloves}{garlic}{crushed}
		and
		\ve{400}{g}{mushrooms}{sliced}.
	\st	Stir in
		\gr{195}{g}{whole grain mustard}{}
		and the pasta,
		and warm through.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Coconut dal}%
{%
	\st	\rice.
	\st	In a \pan cook
		\gr{225}{g}{red lentils}{}
		\ch{1}{tbsp}{ground turmeric}{},
		\ve{4}{cm}{ginger}{chopped}
		and
		\ve{200}{g}{onion}{chopped}
		in
		\wa{600}{ml}{water}{}
		until soft.
	\st	In a \wok fry
		\gr{100}{g}{dessicated coconut}{}
		in
		\ch{1}{tbsp}{oil}{}
		until it goes brown.
	\st	Sprinkle the coconut on the dal
		before serving
		and
		serve with
		\ve{1}{}{lemon}{sliced}.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Parsnip and bacon}
{%
	\st	Steam or microwave
		\ve{800}{g}{parsnips}{sliced}
		and then roll in
		\ch{2}{tsp}{paprika}{}.
	\st	In a \wok fry
		\me{100}{g}{bacon}{chopped} 
		and the parsnips in
		\ch{1}{tbsp}{oil}{}
		until the bacon done.
	\st	Stir in
		\gr{4}{tbsp}{bread crumbs}{}.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Ethiopian peanut stew}%
{%
	\st	\rice.
	\st	In a \wok,
		fry,
		in \ch{2}{tbsp}{oil}{}
		\ve{200}{g}{onions}{chopped},
		until soft.
	\st	Stir in
		\ch{1}{tbsp}{curry powder}{}
		and
		\gr{150}{g}{tomato puree}{}
		and cook for 5 minutes.
	\st	Stir in
		\gr{350}{g}{peanut butter}{}
		and
		\wa{350}{ml}{water}{}
		and simmer for 15 minutes uncovered.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Scramble egg and peppers}%
{%
	\st	In a \wok fry
		\ve{2}{cloves}{garlic}{crushed}, 
		\ve{500}{g}{onions}{chopped},
		\ve{300}{g}{green peppers}{sliced}
		and
		\me{200}{g}{bacon}{chopped}
		in
		\da{10}{g}{butter}{}
		and
		\ch{2}{tbsp}{oil}{}
		until onions are soft.
	\st	Stir in
		\gr{400}{g}{canned tomatoes}{chopped},
		\ch{1}{tbsp}{dried basil}{}
		and
		simmer for 5 minutes.
	\st	Stir in 
		\da{4}{}{eggs}{beaten}
		and keep stirring until cooked.
}

\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Paprika pork}% Judith Parry-Evans
{%
	\st	\rice.
	\st	In a \wok in
		\ch{2}{tbsp}{oil}{}
		fry
		\ve{400}{g}{onions}{chopped},
		\ve{3}{cloves}{garlic}{crushed}
		and
		\me{400}{g}{pork}{cubed}
		until the pork is done.
	\st	Stir in 
		\ch{2}{tbsp}{flour}{}
		and
		\ch{2}{tsp}{paprika}{}.
	\st	Stir in
		\ve{2}{}{red peppers}{chopped},
		\ch{1}{cube}{stock}{crumbled},
		and
		\wa{500}{ml}{water}{}
		and simmer until done.
	\st	Pour on
		\da{150}{ml}{natural yoghurt}{}
		before serving.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Potatoes Swedish style}% Usenet
{%
	\index{Style!Swedish potatoes}
	\st	In a \cass layer
		\ve{2000}{g}{potatoes}{sliced},
		\ve{350}{g}{onions}{chopped},
		\gr{200}{g}{anchovy fillets}{}
		and
		\ve{25}{g}{butter}{}.
	\st Pour over		
		\da{300}{ml}{single cream}{}.
	\st	Sprinkle with
		\gr{4}{tbsp}{bread crumbs}{}.
	\st	Bake \med for 50 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Cheese Cous Cous}% Jackie Knights
{%
	\st	In a \cass bake
		\ve{400}{g}{courgettes}{sliced},
		\ve{350}{g}{onions}{sliced},
		\ve{150}{g}{red peppers}{sliced},
		\ve{150}{g}{green peppers}{sliced},
		\ve{400}{g}{aubergine}{sliced}
		in
		\ch{2}{tbsp}{olive oil}{}
		for 30 minutes.
	\st	Stir in
		\ve{100}{g}{tomatoes}{chopped},
		\gr{50}{g}{capers}{},
		\da{200}{g}{halloumi cheese}{chopped},
		\gr{100}{g}{olives}{chopped}
		and bake for 10 minutes.
	\st	\couscous
	\st	In a \wok mix
		\ch{2}{tbsp}{olive oil}{},
		juice of 
		\ve{1}{}{lime}{},
		\ch{1}{tbsp}{ground cumin}{},
		\gr{75}{g}{tomato puree}{},
		\ch{2}{tsp}{onion seeds}{}
		and warm through.
	\st	Put the vegetables on to the cous cous.
		Then a layer of
		\ve{1}{}{lettuce}{chopped}.
		Then the olive oil mixture.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Spaghetti Hoops}%
{%
	\st	In a \pan warm
		\gr{400}{g}{canned spaghetti hoops}{}
		and serve on
 		\gr{4}{slices}{granary bread}{}.

}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Fish Curry}%
{%
	\index{Curry!Fish}
	\st	In a \cass mix
		\me{500}{g}{fish}{chopped},
		\ve{350}{g}{onions}{chopped},
		\ve{200}{g}{apples}{chopped},
		\gr{2}{tbsp}{tomato puree}{},
		\gr{2}{tbsp}{pickle/chutney}{},
		\gr{400}{g}{canned tomatoes}{chopped}
		and
		\ch{1}{tbsp}{curry powder}{},
		bake \med for 30 minutes.
	\st	\couscous.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Penang Rice Noodles}% Ken Hom
{%
	\st	In a pan soak
		\gr{400}{g}{rice noodles}{}
		in
		\wa{1}{l}{water}{warm}
		for 25 minutes then drain.
	\st	In a \wok in
		\gr{2}{tbsp}{oil}{}
		fry
		\ve{2}{cloves}{garlic}{crushed},
		\ve{300}{g}{onions}{sliced},
		\ve{100}{g}{spring onions}{chopped},
		\ve{200}{g}{chinese green leafs}{hacked}
		and
		\ve{100}{g}{chives}{chopped}
		until wilted.
	\st	Add the noodles,
		\gr{2}{tbsp}{soya sauce}{},
		\gr{1}{tbsp}{dry sherry}{},
		\gr{2}{tbsp}{oyster sauce}{}
		and
		\gr{1}{tbsp}{sesame oil}{}
		and warm through.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Egg Curry}% From Metro News
{%
	\index{Curry!Egg}
	\st	In a \wok fry
		\ve{350}{g}{onions}{chopped}
		and
		\ve{3}{cloves}{garlic}{crushed}		
		in 
		\ch{2}{tbsp}{oil}{}
		until soft.
	\st	Stir in
		\ch{1}{tbsp}{curry powder}{}
		and warm through.
	\st	Stir into the 
		\gr{150}{g}{tomato puree}{}
		and
		\gr{400}{g}{canned tomatoes}{chopped}
		and simmer 20 minutes.
	\st	\rice.
	\st	Break
		\da{4}{}{eggs}{}
		into the curry and simmer until set.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Mackerel on bread}%
{%
	\st	Grill
		\me{400}{g}{smoked mackerel fillet}{}
		and serve with
 		\gr{6}{slices}{granary bread}{}
		and
		\da{20}{g}{butter}{}.
}%

\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Meat and Pasta Stew}% Nigella Lawson
{%
	\index{Stew!Meat and Pasta}
	\st	In a \pan fry
		\me{400}{g}{meat}{chopped}
		in
		\ch{2}{tbsp}{oil}{}
		until done.
	\st	Stir in 
		\gr{400}{g}{canned tomatoes}{chopped},
		\ve{400}{g}{carrots}{chopped},
		\wa{500}{ml}{water}{},
		\ch{10}{tbsp}{sherry}{},
		\ch{1}{}{stock cube}{crumbled}
		and	
		\ve{800}{g}{frozen peas}{}
		and simmer for 20 minutes.
	\st	Stir in
		\gr{400}{g}{pasta shells}{}
		simmer for 15 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Fletch's Chicken Curry}% Simon Fletcher
{%
	\index{Curries!Chicken}
	\st	In a \cass mix
		\me{500}{g}{chicken}{chopped},
		\ve{350}{g}{onions}{chopped},
		\ve{200}{g}{apples}{chopped},
		\gr{150}{g}{tomato puree}{},
		\gr{2}{tbsp}{pickle/chutney}{},
		\gr{400}{g}{canned tomatoes}{chopped}
		and
		\ch{1}{tbsp}{curry powder}{},
		bake \med\ for 30 minutes.
	\st	\rice.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Peas and Rice}% The Guardian Weekend
{%
	\st	In a \wok fry
		\ve{350}{g}{onions}{chopped}
		in 
		\da{80}{g}{butter}{}
		until soft.
	\st	Stir in
		\gr{800}{g}{frozen peas}{},
		\ch{1}{cube}{stock}{crumbled}
		\gr{400}{g}{rice}{}
		and
		\wa{800}{g}{water}{}
		and simmer until rice done.
	\st	Before serving stir in
		\gr{50}{g}{grated parmesan}{}.
	
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Anchovy Spaghetti}% Bill Collinge
{%
	\st	\halfpasta{spaghetti}.
	\st	In a \wok fry
		\ve{1}{clove}{garlic}{crushed}
		and
		\ve{1}{}{red chilli}{chopped}
		in
		\ch{2}{tbsp}{oil}{}
		until brown.
	\st	Stir in
		\gr{150}{g}{tomato puree}{},
		\gr{400}{g}{canned tomatoes}{chopped},
		\gr{100}{g}{anchovy fillets}{chopped},
		\gr{100}{g}{olives}{chopped}
		and
		\gr{50}{g}{capers}{}
		and simmer for 10 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Sausage Spaghetti}% The Godfather
{%
	\st	\pasta{spaghetti}.
	\st	In a \wok simmer
		\ve{1}{clove}{garlic}{crushed},
		\ch{2}{tbsp}{oil}{},
		\gr{150}{ml}{wine}{},
		\gr{150}{g}{tomato puree}{},
		\ch{1}{tsp}{mixed herbs}{},
		\gr{400}{g}{canned tomatoes}{chopped}
		and
		\me{400}{g}{sausages}{chopped}
		until sausages done.	
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Lentil Hotpot}% Vegan Health Plan page 205
{%
	\st	In a \wok fry
		\ve{350}{g}{onions}{chopped},
		\ve{150}{g}{red peppers}{chopped},
		\ve{400}{g}{celery}{chopped},
		\ve{300}{g}{fennel}{chopped}
		\ve{100}{g}{mushrooms}{chopped}
		and
		\ve{2}{clove}{garlic}{crushed}
		in
		\ch{2}{tbsp}{oil}{}
		until soft.
	\st	In a \cass layer
		\gr{225}{g}{red lentils}{},
		\ch{3}{tsp}{mixed herbs}{}
		and vegetable tomato mix 3 times.
	\st	Layer \ve{500}{g}{potatoes}{sliced} on top.
	\st	Pour on 
		\ch{2}{tsp}{miso}{}
		dissolved in 
		\wa{500}{g}{water}{warm},
	\st	Bake \med for 50 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Bean and Nut Roast}% Vegan Health Plan page 122
{%
	\st	\spud.
	\st	In a \wok fry
		\ve{350}{g}{onions}{chopped},
		and
		\ve{1}{clove}{garlic}{crushed}
		in
		\ch{2}{tbsp}{oil}{}
		until soft.
	\st	Stir in 
		\gr{100}{g}{nuts}{chopped},
		\gr{4}{tbsp}{bread crumbs}{},
		\gr{75}{g}{tomato puree}{},
		\ch{3}{tsp}{miso}{},
		\gr{2}{tbsp}{pickle/chutney}{},
		\ch{2}{tbsp}{whole grain mustard}{},
		\ch{1}{tsp}{ground cumin}{},
		\ch{1}{tsp}{ground coriander}{}
		and 
		\ch{1}{tsp}{garam masala}{}.
	\st	Stir in 
		\gr{400}{g}{canned beans}{mashed}
		and mix well.
	\st	Put in a \cass and
		bake \med for 45 minutes.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\quick{Chilli Spaghetti}% Birmingham Metro News
{%
	\st	\halfpasta{spaghetti}.
	\st	In a \wok fry
		\ve{1}{}{chilli}{chopped},
		\ve{1}{clove}{garlic}{crushed}
		in
		\ve{1}{tbsp}{olive oil}{}
		and
		\ve{25}{g}{butter}{}
		for 1 minute.
	\st	Stir in 
		the juice of
		\ve{1}{}{lemon}{}
		and
		\ch{1}{tsp}{basil}{}.
}%

\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{Summer Solstice}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Recipe}%
{%
	\st \rice.
}%
\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Recipe}%
{%
	\st \rice.
}%
\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Recipe}%
{%
	\st \rice.
}%
\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{End of Summer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Recipe}%
{%
	\st \rice.
}%
\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\season{Autumn}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{Beginning of Autumn}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Recipe}%
{%
	\st \rice.
}%
\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Recipe}%
{%
	\st \rice.
}%
\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{Autumn Equinox}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Recipe}%
{%
	\st \rice.
}%
\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Recipe}%
{%
	\st \rice.
}%
\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Recipe}%
{%
	\st \rice.
}%
\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{menu}{End of Autumn}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipe{Recipe}%
{%
	\st \rice.
}%
\end{menu}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\notes{Recipes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\printindex

\end{document}